working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-14 Manuscript_draft/Manuscript_draft.Rmd
edits

#IPPU
load("effect_size_species/ippu_effect_size.RData")
p6<- ggplot(ippu_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+
  theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_blank())+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("F) I. purpurea")

#CAAN
load("effect_size_species/caan_effect_size.RData")
p7<- ggplot(caan_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'bold', 'italic','italic', 'italic', 'italic', 'italic', 'italic')))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("G) C. annuum")

#PEIN
load("effect_size_species/pein_effect_size.RData")
p8<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = unit(c(0.3,0,0,0.5), "cm"))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("H) P. integrifolia")

#SOLY
load("effect_size_species/soly_effect_size.RData")
p9<- ggplot(soly_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'bold', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'italic')),plot.margin = unit(c(0.3,0,0,0.5), "cm"))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("I) P. integrifolia")

@@

p10<- ggplot(some_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_blank())+ geom_point(size=2,alpha=c(1,1,1,1,1,1,1,1,1,1),show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("J) P. integrifolia")

>>>>

#IPPU
load("effect_size_species/ippu_effect_size.RData")
p6<- ggplot(ippu_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+
  theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_blank())+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("F)",italic('I. purpurea'))))

#CAAN
load("effect_size_species/caan_effect_size.RData")
p7<- ggplot(caan_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'bold', 'italic','italic', 'italic', 'italic', 'italic', 'italic')))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("G)",italic('C. annuum'))))

#PEIN
load("effect_size_species/pein_effect_size.RData")
p8<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = unit(c(0.3,0,0,0.5), "cm"))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("H)",italic('P. integrifolia'))))

#SOLY
load("effect_size_species/soly_effect_size.RData")
p9<- ggplot(soly_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'bold', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'italic')),plot.margin = unit(c(0.3,0,0,0.5), "cm"))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("I)",italic('S. lycopersicum'))))

@@

p10<- ggplot(some_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_blank())+ geom_point(size=2,alpha=c(1,1,1,1,1,1,1,1,1,1),show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("J)",italic('S. melongena'))))
